# PERMANOVA + beta dispersion + Ordination

**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


## PERMANOVA
```{r, warning=FALSE, message=FALSE}
dada2_ps_per <- run_permanova(ps = dada2_ps_rare_genus, 
                              method = "bray", 
                              columns = "Group")
print(dada2_ps_per)
```

The PERMANOVA result of the Group (AdjustedPvalue > 0.05) revealed that the two groups had not the distinct patterns of microbial community.

## beta dispersion 
```{r}
beta_df <- run_beta_diversity(ps = dada2_ps_rare_genus, 
                              method = "bray", 
                              group = "Group")
```


## Ordination

We performed ordination by using Principal Coordinate Analysis (PCoA). If you want to try other methods please go to see **Chapter 8** for more details.
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=8, fig.align="center", fig.cap="PCoA (16s example)"}
dada2_ps_ordination <- run_ordination(
                           ps = dada2_ps_rare_genus,
                           group = "Group",
                           method = "PCoA")

plot_Ordination(ResultList = dada2_ps_ordination, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"))
```

## Systematic Information
```{r}
devtools::session_info()
```
