# Microbial composition

**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
```


A whole picture of the microbial composition.

## Stacked barplot 

* **XVIZ** package
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=9, fig.align="center", fig.cap="Microbial composition (16s example) XVIZ"}
plot_stacked_bar_XIVZ(
        phyloseq = dada2_ps_rare,
        level = "Phylum",
        feature = "Group")
```


* **XMAS** package
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=7, fig.align="center", fig.cap="Microbial composition (16s example)"}
plot_StackBarPlot(
        ps=dada2_ps_rare,
        taxa_level="Phylum",
        group = "Group",
        cluster = TRUE)
```

## Core microbiota

* convert absolute abundance into relative abundance 
```{r, warning=FALSE, message=FALSE}
dada2_ps_rare_rb <- XMAS2::normalize(dada2_ps_rare, method = "TSS")
dada2_ps_rare_rb
```

* visualization
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=7, fig.align="center", fig.cap="Core taxa (16s example)"}
prevalences <- seq(0.05, 1, 0.05)
detections <- 10^seq(log10(1e-3), log10(0.2), length = 10)

pl_core <- plot_core_taxa(dada2_ps_rare_rb, 
                    plot.type = "heatmap", 
                    colours = gray(seq(0, 1, length=5)),
                    prevalences = prevalences, 
                    detections = detections, 
                    min.prevalence = 0.5)+
    xlab("Detection Threshold (Relative Abundance (%))")

pl_core
```

The degree of color indicates the size of abundance and prevalence.

* Use `core_members` to obtain the core taxa. detection for abundance and prevalence for occurrence.
```{r, warning=FALSE, message=FALSE}
core_taxa_name <- core_members(dada2_ps_rare_rb, detection = 0.01, prevalence = 0.8)
print(core_taxa_name)
```

**Result**:

Only 2 genera (g__Bifidobacterium and g__Blautia) passed the threshold of detection and prevalence which we choose.

## Systematic Information
```{r}
devtools::session_info()
```