# Differential Analysis


**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


There are more than 10 approaches to perform differential analysis. Here, we choose two of them and recommend users going to **[XMAS2: Chapter 11](https://xbiomeanalysis.github.io/XMAS_tutorial/differential-analysis.html)** to see more details.


## Filtering and trimming

We suggest that filtering taxa with low abundance (the summarized value under cutoff: `10`) and trimming taxa with low prevalence (default: `0.1`).

### Filtering the low relative abundance or unclassified taxa by the threshold (total counts < 10)
```{r, warning=FALSE, message=FALSE}
dada2_ps_rare_genus_filter <- run_filter(ps = dada2_ps_rare_genus, 
                                         cutoff = 10, 
                                         unclass = TRUE)
dada2_ps_rare_genus_filter 
```

### Trimming the taxa with low occurrence less than threshold
```{r, warning=FALSE, message=FALSE}
dada2_ps_rare_genus_filter_trim <- run_trim(object = dada2_ps_rare_genus_filter, 
                                            cutoff = 0.1, 
                                            trim = "feature")
dada2_ps_rare_genus_filter_trim
```

Finally, we obtained the final phyloseq-class object _dada2\_ps\_rare\_genus\_filter\_trim_ and changed its name.


## Liner discriminant analysis (LDA) effect size (LEfSe)

* Calculation
```{r, warning=FALSE, message=FALSE}
dada2_ps_lefse <- run_lefse(
                      ps = dada2_ps_rare_genus_filter_trim,
                      group = "Group",
                      group_names = c("AA", "BB"),
                      norm = "CPM",
                      Lda = 2)
head(dada2_ps_lefse)
```

* Visualization
```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4, fig.align="center", fig.cap="Lefse analysis (16s example)"}
# # don't run this code when you do lefse in reality
# dada2_ps_lefse$LDA_Score <- dada2_ps_lefse$LDA_Score * 1000

plot_lefse(
    da_res = dada2_ps_lefse,
    x_index = "LDA_Score",
    x_index_cutoff = 2,
    group_color = c("green", "red"))
```


## Wilcoxon Rank-Sum test

* Calculation
```{r, warning=FALSE, message=FALSE}
dada2_ps_wilcox <- run_wilcox(
                      ps = dada2_ps_rare_genus_filter_trim,
                      group = "Group",
                      group_names = c("AA", "BB"))

head(dada2_ps_wilcox)
```


* Volcano
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.align="center", fig.cap="Wilcoxon Rank-Sum test (16s example)"}
plot_volcano(
    da_res = dada2_ps_wilcox,
    group_names = c("AA", "BB"),
    x_index = "Log2FoldChange (Rank)\nAA_vs_BB",
    x_index_cutoff = 0.5,
    y_index = "Pvalue",
    y_index_cutoff = 0.05,
    group_color = c("red", "grey", "blue"),
    topN = 5)
```


## Dominant taxa

Display the significant taxa with selection using boxplot.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=5, fig.cap="Dominant Taxa"}
plot_topN_boxplot(
    ps = dada2_ps_rare_genus_filter_trim,
    da_res = dada2_ps_wilcox,
    x_index = "Log2FoldChange (Rank)\nAA_vs_BB",
    x_index_cutoff = 0.5,
    y_index = "Pvalue",
    y_index_cutoff = 0.05,
    topN = 5,
    group = "Group")
```


## Multiple differential analysis by one function

here, we provide the `run_multiple_da` for obtaining the results list from multiple differential analysis methods.

```{r, warning=FALSE, message=FALSE}
multiple_res <- run_multiple_da(
                   ps = dada2_ps_rare_genus_filter_trim,
                   group = "Group",
                   group_names = c("AA", "BB"),
                   da_method = c("aldex", "limma_voom", "mbzinb", "omnibus"))

names(multiple_res)
```


* plot  results
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=13, fig.cap="Multiple DA results"}
plot_multiple_DA(
    Multip_DA_res = multiple_res,
    x_index_list = c("EffectSize", "logFC", "mean.LFC", "abund.LFC.CompvarBB.est"),
    x_index_cutoff = 1,
    y_index = "AdjustedPvalue",
    y_index_cutoff = 0.5,
    cellwidth = 50, 
    cellheight = 15, 
    fontsize_number = 15)
```


## Systematic Information
```{r}
devtools::session_info()
```

