# Differential Analysis


**Loading packages**
```R
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
```


There are more than 10 approaches to perform differential analysis. Here, we choose two of them and recommend users going to **Chapter 10** to see more detials.

## Liner discriminant analysis (LDA) effect size (LEfSe)

* Calculation
```{r, warning=FALSE, message=FALSE}
dada2_ps_lefse <- run_lefse(
                    dada2_ps_final,
                    group = "Group",
                    group_names = c("AA", "BB"),
                    transform = "identity",
                    norm = "none",
                    wl.p = 0.05,
                    Lda = 0)
head(dada2_ps_lefse)
```

* Visualization
```{r, warning=FALSE, message=FALSE, fig.width=6, fig.height=4, fig.align="center", fig.cap="Lefse analysis (16s example)"}
# in order to show barplot (don't run it in reality)
dada2_ps_lefse$LDA_Score <- dada2_ps_lefse$LDA_Score * 1000
plot_lefse(
  da_res = dada2_ps_lefse,
  x_index = "LDA_Score",
  x_index_cutoff = 2,
  group_color = c("green", "red"))
```


## Wilcoxon Rank-Sum test

* Calculation
```{r, warning=FALSE, message=FALSE}
dada2_ps_wilcox <- run_wilcox(
                    dada2_ps_final,
                    group = "Group",
                    group_names = c("AA", "BB"),
                    transform = "identity",
                    norm = "none",
                    p_adjust = "BH",
                    pvalue_cutoff = 0.05)

head(dada2_ps_wilcox)
```


* Volcano
```{r, warning=FALSE, message=FALSE, fig.width=8, fig.height=6, fig.align="center", fig.cap="Wilcoxon Rank-Sum test (16s example)"}
plot_volcano(
    dada2_ps_wilcox,
    group_names = c("AA", "BB"),
    x_index = "Log2FoldChange (Rank)\nAA_vs_BB",
    x_index_cutoff = 0.5,
    y_index = "Pvalue",
    y_index_cutoff = 0.05,
    group_color = c("red", "grey", "blue"),
    topN = 5)
```


## Dominant taxa

Display the significant taxa with selection using boxplot.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=3, fig.cap="Dominant Taxa"}
DA_wilcox <- run_wilcox(
   dada2_ps_final,
   group = "Group",
   group_names = c("AA", "BB"),
   transform = "identity",
   norm = "none",
   p_adjust = "BH",
   pvalue_cutoff = 0.05)

plot_topN_boxplot(
    ps = dada2_ps_final,
    da_res = DA_wilcox,
    x_index = "Log2FoldChange (Median)\nAA_vs_BB",
    x_index_cutoff = 0.2,
    y_index = "Pvalue",
    y_index_cutoff = 0.3,
    prevalence = TRUE,
    topN = 3,
    group = "Group")
```


## Multiple differential analysis by one function

here, we provide the `run_multiple_da` for obtaining the results list from multiple differential analysis methods.

```{r, warning=FALSE, message=FALSE}
multiple_res <- run_multiple_da(
       dada2_ps_final,
       group = "Group",
       group_names = c("AA", "BB"),
       da_method = c("aldex", "limma_voom", "mbzinb", "omnibus"),
       norm = "none",
       transform = "identity",
       p_adjust = "none",
       pvalue_cutoff = 0.05)

names(multiple_res)
```


* plot  results
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=13, fig.cap="Multiple DA results"}
plot_multiple_DA(
  Multip_DA_res = multiple_res,
  y_index = "AdjustedPvalue",
  y_index_cutoff = 0.5,
  cellwidth = 35,
  cellheight = 10,
  fontsize_number = 15)
```


## Systematic Information
```{r}
sessionInfo()
```

