# Data processing



**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
```

This part has too may procedures and we only choose some of them. Please go to **[XMAS tutorial: Chapter 6](https://xbiomeanalysis.github.io/XMAS_tutorial/pre-processing.html)** to see more approaches and details for being familiar with this part.

## Rarefy otu counts

From previous results of quality evaluation, the sequence depth of samples are different which have effects on the downstream analysis. Here, choosing the **rarefy** (Normaliztion method: random subsampling counts to the smallest library size) to get the equal sample sums.

```{r, warning=FALSE, message=FALSE}
dada2_ps_rare <- norm_rarefy(object = dada2_ps_remove_BRS, 
                             size = 51181)
dada2_ps_rare
```

In addition, we could also perform some other normalization methods on the rarefied phyloseq object. By the way, we didn't transform the data by using log algorithm because the count matrix is required by the following data analysis methods.

## Extracting specific taxonomic level
```{r, warning=FALSE, message=FALSE}
dada2_ps_rare_genus <- summarize_taxa(ps = dada2_ps_rare, 
                                      taxa_level = "Genus")
dada2_ps_rare_genus
```

## Systematic Information
```{r}
devtools::session_info()
```